Simulation-WTCCC

### 2019-11-25 analysis/simulation-WTCCC.Rmd
X tilde

## Simulate cis-expression 
We simulate cis- expression based on the following model:

@@

### 1.2 $PVE_{SNP}\approx 0.1$, $PVE_{expr}\approx 0.4$
```{r 1.2}
show_res("S1.2")
```

@@

### 2.2 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.4$
```{r 2.2}
show_res("S2.2")
```
## Simulation 3: $M$ = ~ 10% all SNPs (M=50000), $J$ = No. all genes

@@

### 3.2 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.4$
```{r 3.2}
show_res("S3.2")
```

## Simulation 4: $M$ = ~ 10% all SNPs (M=50000), $J$ = ~10% all genes (J=2000)

@@

### 4.2 $PVE_{SNP} \approx 0.1$, $PVE_{expr} \approx 0.4$
```{r 4.2}
show_res("S4.2")
```

>>>>

## Simulate cis-expression 
We simulate cis-expression based on the following model:

@@

### 1.2 $PVE_{SNP}\approx 0.4$, $PVE_{expr}\approx 0.1$
```{r 1.2}
show_res("S1.2")
```

@@

### 2.2 $PVE_{SNP} \approx 0.4$, $PVE_{expr} \approx 0.1$
```{r 2.2}
show_res("S2.2")
```
## Simulation 3: $M$ = ~ 1% all SNPs (M=5000), $J$ = No. all genes

@@

### 3.2 $PVE_{SNP} \approx 0.4$, $PVE_{expr} \approx 0.1$
```{r 3.2}
show_res("S3.2")
```

## Simulation 4: $M$ = ~ 1% all SNPs (M=5000), $J$ = ~10% all genes (J=2000)

@@

### 4.2 $PVE_{SNP} \approx 0.4$, $PVE_{expr} \approx 0.1$
```{r 4.2}
show_res("S4.2")
```
